---
title: "EFMW Study 1 PreLiminary Analysis"
creation date: "August 10, 2023"
last edited date: "January 12, 2024"
author: "Chelsie H."
output: html_notebook
---

Note: This R script assumes combined data has been processed through ScoreConversions.Rmd

```{r startup}
rm()

library(correlation)
library(ggplot2)
library(sjPlot)
library(lme4)
library(lmerTest)
library(rstatix)


versions <- devtools::session_info() #save R and R package versions.
versions
```

```{r load data}
directoryset = readline("Are you using the PC (1) or Laptop (2)?")

if (directoryset == "1"){
  setwd("C:/Users/chish/OneDrive - University of Calgary/1_PhD_Project/Scripting/RPSPreliminaryAnalysis")
} else {
  setwd("C:/Users/chels/OneDrive - University of Calgary/1_PhD_Project/Scripting/RPSPreliminaryAnalysis")
}

AllData <- read.csv("RPSCombinedDataConv_Jan12_2024.csv")

rm(directoryset)
```

Assumption Checks

(outlier code taken from: https://stackoverflow.com/questions/33524669/labeling-outliers-of-boxplots-in-r)

```{r assumption checks for ASRS}
hist(AllData$ASRSTotal)
shapiro.test(AllData$ASRSTotal)
qqnorm(AllData$ASRSTotal)

ggplot(AllData, aes(y = ASRSTotal)) +
  geom_boxplot()
```
Histogram: slight positive skew
Shapiro-Wilk: W = 0.97953, p-value = 0.0373
QQ: mostly straight line
Boxplot: outliers at top and bottom, but mostly equal.

ASRS is normal enough.

```{r ASRS identify outlier}
AllData %>%
  identify_outliers(ASRSTotal)
```


```{r assumption checks for BDEFS}
hist(AllData$TotalBDEFS)
shapiro.test(AllData$TotalBDEFS)
qqnorm(AllData$TotalBDEFS)

ggplot(AllData, aes(y = TotalBDEFS)) +
  geom_boxplot()

BDEFSOutlier = AllData[AllData$TotalBDEFS == max(AllData$TotalBDEFS),]
```
Histogram: 
Shapiro-Wilk: 
QQ:
boxplot:

BDEFS does not pass normality potentially due to one high outlier.

```{r BDEFS identify outlier}
AllData %>%
  identify_outliers(TotalBDEFS)
```


```{r assumption checks for Mews}
hist(AllData$TotalMews)
shapiro.test(AllData$TotalMews)
qqnorm(AllData$TotalMews)

ggplot(AllData, aes(y = TotalMews)) +
  geom_boxplot()
```

Histogram: 
Shapiro-Wilk: 
QQ:
boxplot:

Mews is skewed towards lower scores (positive skew)

```{r assumption checks for SARTz}
hist(AllData$SARTz)
shapiro.test(AllData$SARTz)
qqnorm(AllData$SARTz)

ggplot(AllData, aes(y = SARTz)) +
  geom_boxplot()
```

Histogram: 
Shapiro-Wilk: 
QQ:
boxplot:

SARTz is skewed towards higher scores (negative skew)
Checking raw scores
```{r assumption checks for SARTdPrime}
hist(AllData$SARTdPrime)
shapiro.test(AllData$SARTdPrime)
qqnorm(AllData$SARTdPrime)

ggplot(AllData, aes(y = SARTdPrime)) +
  geom_boxplot()
```

Histogram: 
Shapiro-Wilk: 
QQ:
boxplot:

Skew was present in raw data.

```{r assumption checks for Switchz}
hist(AllData$Switchz)
shapiro.test(AllData$Switchz)
qqnorm(AllData$Switchz)

ggplot(AllData, aes(y = Switchz)) +
  geom_boxplot()
```

Histogram: 
Shapiro-Wilk: 
QQ:
boxplot:

Switchz has a few high outliers likely causing it to not pass normality assumption checks

```{r Switchz identify outlier}
AllData %>%
  identify_outliers(Switchz)
```

```{r assumption checks for WMComp}
hist(AllData$WMComp)
shapiro.test(AllData$WMComp)
qqnorm(AllData$WMComp)

ggplot(AllData, aes(y = WMComp)) +
  geom_boxplot()
```

Histogram: 
Shapiro-Wilk: 
QQ:
boxplot:

WM composite does not pass assumption checks. Skew towards higher scores (negative skew)

```{r assumption checks for MCTMWRate}
hist(AllData$MCTMWRate)
shapiro.test(AllData$MCTMWRate)
qqnorm(AllData$MCTMWRate)

ggplot(AllData, aes(y = MCTMWRate)) +
  geom_boxplot()
```

Histogram: 
Shapiro-Wilk: 
QQ:
boxplot:

MW rate is not normally distributed.


```{r assumption checks for MCTAwareRate}
hist(AllData$MCTAwareRate)
shapiro.test(AllData$MCTAwareRate)
qqnorm(AllData$MCTAwareRate)

ggplot(AllData, aes(y = MCTAwareRate)) +
  geom_boxplot()
```

Histogram: 
Shapiro-Wilk: 
QQ:
boxplot:

Aware rate not normally distributed

```{r assumption checks for MCTIntentRate}
hist(AllData$MCTIntentRate)
shapiro.test(AllData$MCTIntentRate)
qqnorm(AllData$MCTIntentRate)

ggplot(AllData, aes(y = MCTIntentRate)) +
  geom_boxplot()
```

Histogram: 
Shapiro-Wilk: 
QQ:
boxplot:

Intentional rate not normally distributed

```{r mahalanobis distance all variables of interest}
mahalanobis_distance(AllData[,c(30,31,34,186,187,191:194)])
```

```{r mahalanobis distance without questionnaire scales}
mahalanobis_distance(AllData[,c(186,187,191:194)])
```

```{r mahalanobis distance EF measures}
mahalanobis_distance(AllData[,c(186,187,191)])
```
One outlier SARTz = -0.223225573 , Switchz = 3.934119854	, WMComp = -1.145909522 ;
same outlier is also in Switchz outliers.

```{r mahalanobis distance MW measures}
mahalanobis_distance(AllData[,c(192:194)])
```

check correlations between scales and tasks
check correlations between EF z-scores
For ASRS use ASRSTotal
For BDEFS use TotalBDEFS
For Mews use TotalMews
```{r correlations}
# attempting with correlation package
# assuming column numbers are constant
# running spearman since many variables rea not normally distributed.
CorrelationChecks <- correlation(AllData[,c(30,31,34,186,187,191:194)],method = "spearman")
CorrelationChecks
```

ASRS positively correlates with BDEFS, MEWS, and mind wandering rate
BDEFS positively correlates with MEWS
SARTz positively correlates with working memory composite
MW rate negatively correlates with aware and intentional rates.
Intentional and aware rates are positively correlated.

Questionnaire scales do not correlate with EF measures, but correlate with each other.
Some intercorrelation between EF measures.
mind wandering rate only correlates with ASRS (and other mind wandering aspect rates)

regression analyses with part and partial correlations
MW ~ EF variables

```{r mw rate and ef scores}
MWEF <- lm(MCTMWRate ~ SARTz + Switchz + WMComp, AllData)
summary(MWEF)
plot_model(MWEF, type = "diag")
```
EF z scores and composite do not predict MW rate.

Intentional ~ EF
```{r intentional mw rate and ef scores}
IntentEF <- lm(MCTIntentRate ~ SARTz + Switchz + WMComp, AllData)
summary(IntentEF)
plot_model(IntentEF, type = "diag")
```
EF z scores and composite do not predict intentional MW rate.

Aware ~ EF
```{r aware mw rate and ef scores}
AwareEF <- lm(MCTAwareRate ~ SARTz + Switchz + WMComp, AllData)
summary(AwareEF)
plot_model(AwareEF, type = "diag")
```
EF z scores and composite do not predict aware MW rate.

