---
title: "EFMW Study 1 Score Conversions"
creation date: "August 10, 2023"
last edited date: "January 12, 2024"
author: "Chelsie H."
output: html_notebook
---

```{r startup}
versions <- devtools::session_info() #save R and R package versions.
versions
```

```{r load data}
directoryset = readline("Are you using the PC (1) or Laptop (2)?")

if (directoryset == "1"){
  setwd("C:/Users/chish/OneDrive - University of Calgary/1_PhD_Project/Scripting/RPSPreliminaryAnalysis")
} else {
  setwd("C:/Users/chels/OneDrive - University of Calgary/1_PhD_Project/Scripting/RPSPreliminaryAnalysis")
}

AllData <- read.csv("RPSCombinedData_January11_2024.csv")
```

z-score EF tasks
SART score is d' (SARTdPrime)
Switch score is reaction time cost (SwitchCostRT)
Symmetry Span scores is partial score (SymSpanAccuracy)
1-back score is d' (NBack1DPrime)
2-back score is d' (NBack2DPrime)
```{r calculate means and sds}
SARTmean <- mean(AllData$SARTdPrime, na.rm = TRUE)
SARTsd <- sd(AllData$SARTdPrime, na.rm = TRUE)

Switchmean <- mean(AllData$SwitchCostRT, na.rm = TRUE)
Switchsd <- sd(AllData$SwitchCostRT, na.rm = TRUE)

SymSpanmean <- mean(AllData$SymSpanAccuracy, na.rm = TRUE)
SymSpansd <- sd(AllData$SymSpanAccuracy, na.rm = TRUE)

Nback1mean <- mean(AllData$NBack1DPrime, na.rm = TRUE)
Nback1sd <- sd(AllData$NBack1DPrime, na.rm = TRUE)

Nback2mean <- mean(AllData$NBack2DPrime, na.rm = TRUE)
Nback2sd <- sd(AllData$NBack2DPrime, na.rm = TRUE)
```

z score = (score - mean)/sd
```{r calculate z-scores}
AllData$SARTz <- (AllData$SARTdPrime - SARTmean)/SARTsd
AllData$Switchz <- (AllData$SwitchCostRT - Switchmean)/Switchsd
AllData$SymSpanz <- (AllData$SymSpanAccuracy - SymSpanmean)/SymSpansd
AllData$Nback1z <- (AllData$NBack1DPrime - Nback1mean)/Nback1sd
AllData$Nback2z <- (AllData$NBack2DPrime - Nback2mean)/Nback2sd
```

Calculate Composites
average symm span and n-backs
```{r calculate composites}
AllData$WMComp <- rowMeans(AllData[,c("SymSpanz","Nback1z","Nback2z")], na.rm = TRUE)
```

Convert MW scores to percentages
Total probes is MCTProbes
Mind wandering is MCTMW
Aware is MCTAware
Intentional is MCTIntentional

```{r MW percentages}
AllData$MCTMWRate <- AllData$MCTMW / AllData$MCTProbes

AllData$MCTAwareRate <- AllData$MCTAware / AllData$MCTProbes

AllData$MCTIntentRate <- AllData$MCTIntentional / AllData$MCTProbes
```

```{r save new data}
todaysdate = readline("Please enter today's date to save scores. (MonDD_YYYY)")

filename = paste("RPSCombinedDataConv_",todaysdate, ".csv", sep = "")

write.csv(AllData,filename,row.names = FALSE)
```

